Taking Linear Logic Apart

### 2018-04-24 doc/tlla2018/main.tex
Some related work

\documentclass[submission,copyright,creativecommons]{eptcs}
\providecommand{\event}{Linearity and TLLA 2018}
\usepackage[fleqn]{amsmath}
\usepackage{amsthm}
\usepackage{nameref,hyperref,cleveref}
\usepackage[inline]{enumitem}
\usepackage{breakurl} % Not needed if you use pdflatex only.
\usepackage{underscore} % Only needed if you use pdflatex.
\usepackage{textcomp,textgreek,upgreek}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\input{preamble-typing}

\title{Taking Linear Logic Apart}
\author{%
  Wen Kokke
  \institute{University of Edinburgh\\ Edinburgh, Scotland}
  \email{wen.kokke@ed.ac.uk}
  \and
  Marco Peressotti
  \institute{University of Southern Denmark\\ Odense, Denmark}
  \email{peressotti@imada.sdu.dk}
  \and
  Fabrizio Montesi
  \institute{University of Southern Denmark\\ Odense, Denmark}
  \email{fmontesi@imada.sdu.dk}}
\def\titlerunning{Taking Linear Logic Apart}
\def\authorrunning{W.\ Kokke, M.\ Peressotti, and F.\ Montesi}

@@

\begin{definition}[Terms]\label{def:cp-terms}
  \[
    \begin{array}{rllrll}
      \tm{P}, \tm{Q}, \tm{R}
           :=& \tm{\cpLink{x}{y}}       &\text{link}
      &  \mid& \tm{\cpCut{x}{P}{Q}}     &\text{parallel composition, ``cut''}
      \\ \mid& \tm{\cpSend{x}{y}{P}{Q}} &\text{``output''}
      &  \mid& \tm{\cpRecv{x}{y}{P}}    &\text{``input''}
      \\ \mid& \tm{\cpHalt{x}}          &\text{halt}
      &  \mid& \tm{\cpWait{x}{P}}       &\text{wait}
      \\ \mid& \tm{\cpInl{x}{P}}        &\text{select left choice}
      &  \mid& \tm{\cpInr{x}{P}}        &\text{select right choice}
      \\ \mid& \tm{\cpCase{x}{P}{Q}}    &\text{offer binary choice}
      &  \mid& \tm{\cpAbsurd{x}}        &\text{offer nullary choice}
    \end{array}
  \]
\end{definition}

@@

\bibliographystyle{eptcs}
\bibliography{main}
\end{document}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:

>>>>

\documentclass[draft,submission,copyright,creativecommons]{eptcs}
\providecommand{\event}{Linearity and TLLA 2018}
\usepackage[british]{babel}
\usepackage[all]{foreign}
\usepackage[fleqn]{amsmath}
\usepackage{amsthm}
\usepackage[inline]{enumitem}
\usepackage{breakurl} % Not needed if you use pdflatex only.
\usepackage{underscore} % Only needed if you use pdflatex.
\usepackage{textcomp,textgreek,upgreek}
\usepackage[
	sectionbib,
	square,
	numbers,
	sort&compress
	]{natbib} % \citet
\usepackage{nameref,hyperref,cleveref}
\hypersetup{
	hidelinks,
	final
}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\input{preamble-typing}

\usepackage[
%	disable,     % hide all todos
	obeyDraft,   % show todos only in draft mode
%	obeyFinal,   % hide todos if in final mode
	textwidth=3cm,
	textsize=small,
]{todonotes}

\title{Taking Linear Logic Apart}
\author{%
  Wen Kokke
  \institute{University of Edinburgh\\ Edinburgh, Scotland}
  \email{wen.kokke@ed.ac.uk}
  \and
  Fabrizio Montesi
  \institute{University of Southern Denmark\\ Odense, Denmark}
  \email{fmontesi@imada.sdu.dk}
  \and
  Marco Peressotti
  \institute{University of Southern Denmark\\ Odense, Denmark}
  \email{peressotti@imada.sdu.dk}}
\def\titlerunning{Taking Linear Logic Apart}
\def\authorrunning{W.\ Kokke, F.\ Montesi, and M.\ Peressotti}

@@

\begin{definition}[Terms]\label{def:cp-terms}
  \[
    \begin{array}{rllrll}
      \tm{P}, \tm{Q}, \tm{R}
           :=& \tm{\cpLink{x}{y}}       &\text{link}
      &  \mid& \tm{\cpCut{x}{P}{Q}}     &\text{parallel composition, ``cut''}
      \\ \mid& \tm{\cpSend{x}{y}{P}{Q}} &\text{output}
      &  \mid& \tm{\cpRecv{x}{y}{P}}    &\text{input}
      \\ \mid& \tm{\cpHalt{x}}          &\text{halt}
      &  \mid& \tm{\cpWait{x}{P}}       &\text{wait}
      \\ \mid& \tm{\cpInl{x}{P}}        &\text{select left choice}
      &  \mid& \tm{\cpInr{x}{P}}        &\text{select right choice}
      \\ \mid& \tm{\cpCase{x}{P}{Q}}    &\text{offer binary choice}
      &  \mid& \tm{\cpAbsurd{x}}        &\text{offer nullary choice}
    \end{array}
  \]
\end{definition}

@@

\section{Related Work}

Since its inception, linear logic was described as the logic of concurrency \citep{girard1987}. Correspondences between the proof theory of linear logic and variants of the $\pi$-calculus emerged soon afterwards \citep{abramsky1994,bellin1994}, by interpreting linear logic propositions as types for channels. Later, linearity inspired also the seminal theories of linear types for the $\pi$-calculus \cite{kobayashi1999} and session types \cite{honda1998}. Even though the two theories do not use exactly linear logic, the work by \citet{dardha2017} shows that the link is still strong enough that session types can be encoded into linear types.

It took more than ten years for a formal correspondence between linear logic and (a variant of) session types to emerge, with the seminal paper by \citet{caires2010}. This then inspired the development of Classical Processes (CP) by \citet{wadler2014}. %, which we have already discussed in the Introduction. %\todo{mention this}

The idea of extending linear logic to hypersequents for typing processes is not new. Specifically, in \cite{carbone18}, the multiplicative-additive fragment of Intuitionistic Linear Logic is extended with hypersequents to type choreographies (global descriptions of process communications). Differently, HCP is based on CLL, uses hypersequents to type processes.
%, and deals also with exponentials and polymorphism. 
The major difference is that the rules for manipulating hypersequents are different w.r.t.~\cite{carbone18}. In particular, hypersequents can be 
formed in \cite{carbone18} only when sequents share resources (\cf our \NOM{H-Mix}), and resource sharing is then explicitly tracked using an additional connection modality (which is not present in \hcp).

%As a consequence, the work in \cite{carbone18} does not support an LTS for the same reasons that we discussed for CP in the Introduction. Adding a connection modality to CT might be interesting for providing an LTS semantics to the choreographies studied in \cite{carbone18}.

\section{Conclusions}
\label{sec:conclusions}

%\bibliographystyle{eptcs}
\bibliographystyle{abbrvnat}
\bibliography{main}
\end{document}
%%% Local Variables:
%%% TeX-master: "main"
%%% End:
